\Large Bayes network classifiers for fRMI

### 2012-09-14 proposal/proposal.tex

>>>>

Participants performed an experiment while laying in an fMRI scanner. The experiment consisted of sets of trials where participants were shown a first stimulus for four seconds, then a blank screen for another four seconds, and then a second stimulus for four seconds, which was followed by a rest period of 15 seconds. For the first half of the trials, a picture was used as first stimulus and a sentence was used as second stimulus, while the second half of trials showed a sentence as the first stimulus and a picture as the second. Participants had four seconds after the second stimulus appeared to indicate that the sentence and picture belonged together, after which the stimulus disappeared. If participants did not press a button the stimulus would disappear after four seconds.
